---
title: "BMI of Students in Scotland Throughout the School Year"
author: "Riley A. Moffat"
institute: "Houghton University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(parsnip)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
library(readxl)
read_excel("../data/bmi.xlsx")
```

```{r}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```


class: center, middle

## My Goal is to find out the relationship between the school years and the weight of the students based on sex.

---

class: inverse, center, middle

# BMI and Weight in Scotland

---

# Glimpsing the Data

```{r}
library(readxl)
bmi <- read_excel("../data/bmi.xlsx")
glimpse(bmi)
```

---

# Modifying My Data

I wanted to combine all the weight variables into one, however, it came out with this.

```{r}
bmi$EpiWeight <- paste(bmi$EpiUnderweight, bmi$EpiHealthyWeight, bmi$EpiOverweight, bmi$EpiObese, bmi$EpiOverweightAndObese)

bmi %>%
  select(SchoolYear, EpiWeight, Sex)
```

---
```{r}
ggplot(data = bmi, aes(x = SchoolYear, y = EpiUnderweight, color = Sex)) +
  geom_point() +
  labs(x = "School Year", y = "Underweight Students", title = "Underweight Students Through the School Year by Sex")
```

---


class: inverse, center, middle

#But this seems too boring, doesn't it?

---

```{r}
ggplot(data = bmi, aes(x = SchoolYear, y = EpiUnderweight, color = Sex)) +
  geom_boxplot() +
  labs(x = "School Year", y = "Underweight Students", title = "Underweight Students Through the School Year by Sex")
```

---

```{r}
ggplot(data = bmi, aes(x = SchoolYear, y = EpiHealthyWeight, color = Sex)) +
  geom_boxplot() +
  labs(x = "School Year", y = "Healthyweight Students", title = "Healtyweight Students Through the School Year by Sex")
```

---

```{r}
ggplot(data = bmi, aes(x = SchoolYear, y = EpiOverweight, color = Sex)) +
  geom_boxplot() +
  labs(x = "School Year", y = "Overweight Students", title = "Overweight Students Through the School Year by Sex")
```

---

```{r}
ggplot(data = bmi, aes(x = SchoolYear, y = EpiObese, color = Sex)) +
  geom_boxplot() +
  labs(x = "School Year", y = "Obese Students", title = "Obese Students Through the School Year by Sex")
```

---

```{r}
ggplot(data = bmi, aes(x = SchoolYear, y = EpiOverweightAndObese, color = Sex)) +
  geom_boxplot() +
  labs(x = "School Year", y = "Overweight and Obese Students", title = "Overweight and Obese Students Through the School Year by Sex")
```
